### 2018-02-13 Writing/Thesis/content/chapter-approach.tex
more writing
more writing + adding some picture

In this chapter the two alternatives which ar

@@

@@

@@

>>>>

In this chapter the two alternatives to tackle the problem of ranking classification algorithms regarding properties of the data set based on past performance values are described in detail. First, the theoretical approach is presented. Then, implementation details are discussed.

@@

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/regression_models.pdf}
\caption{A model of the regression based ranker}
\label{fig:regression_ranker_model}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/label_ranking_model.pdf}
\caption{A model of the preference based ranker}
\label{fig:preference_ranker_model}
\end{figure}

@@

\subsection{Frameworks used}
% Weka for classifiers

% Data sets from OpenML

\subsection{jPL framework}
The jPL framework is a java framework for the evaluation of preference learning algorithms. It implements several tasks from the context of preference learning, including label ranking. Furthermore, the framework introduces the Generic Preference Representation Format (GPRF) to store preference information.

\subsection{WEKA}

% openml Webapp for metaFeature implementation except default accuracy

\section{Generating Performance Values}
Performance values generated by

\section{Stuff}

Rankers trained with data set of the following form, so each ranking algorithm can derive its on performance
